---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# boclust

The goal of boclust is to provide a new normalization method for sparse data by a feature 
boosting strategy with the latent representation, especially for scRNA-seq data consisted of many zeros. Based on the normalization, a new measure of similarity is defined for the following clustering algorithm. Unlike other unsupervised cluster methods, boclust provides the suggestion K to determine the number of clusters. In this way, it may be unsuitable for low-dimentional data. 

There are three major functions:

- BossaSimi: to calculate the similarity matrix and normalized data.
- BossaClust: the main function which provide an object including clustering result for shiny.
- bossa_interactive: a shiny framework to show the clustering result.

## Installation

You can install boclust from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("TinyOpen/boclust")
```

## Example

```{r example, eval = FALSE}
sparse.data <- data.frame(g.1 = c(0, 5, 0, 6, 8, 6, 7, 7), 
                          g.2 = c(5, 0, 0, 0, 5, 7, 5, 7)) # generate sparse data from the toy model of CIDR
bossa.change <- BossaSimi(sparse.data, is.pca = FALSE) # with low-dimensional data, pca is uncessary
data.after <- bossa.change$U.score.non.pca # data after normalization

```

Now, when it comes to your **high-dimentional** data, you can either use `BossaClust' 
to get the final result:

```{r eval = FALSE}
object <- BossaClust(high.dim.data) # do normalization and clustering at the same time
bossa_interactive(object) # use shiny frame to show the result
```

Or, you can store the normalized data first, which is obtained from function 'BossaSimi', 
and then do the rest work.

```{r eval = FALSE}
pre.object <- BossaSimi(high.dim.data)
object <- BossaClust(data = high.dim.data, data.pre = pre.object) # do normalization and clustering at the same time
bossa_interactive(object) # use shiny frame to show the result
```
